A general and efficient representation of ancestral recombination graphs

### 2024-06-04 paper.tex
Fix typo

Aside from these practical challenges, there is also a deeper
issue with the implicit strategy of basing an ARG data structure on
recording events and their properties (e.g.\ the crossover breakpoint
for a recombination event). This approach 
requires all events to be recorded explicitly, and does not 
provide an obvious mechanism for aggregating multiple, potentially
unresolvable, events.
As datasets approach the population scale~\citep[e.g.][]{
turnbull2018hundred, bycroft2018genome,hayes20191000,
Ros-Freixedes2020,karczewski2020mutational,tanjo2021practical,
halldorsson2022sequences} representing such uncertainty 
directly through the data structure is a useful alternative to 
classical methods based on probabilisitic sampling.

>>>>

Aside from these practical challenges, there is also a deeper
issue with the implicit strategy of basing an ARG data structure on
recording events and their properties (e.g.\ the crossover breakpoint
for a recombination event). This approach 
requires all events to be recorded explicitly, and does not 
provide an obvious mechanism for aggregating multiple, potentially
unresolvable, events.
As datasets approach the population scale~\citep[e.g.][]{
turnbull2018hundred, bycroft2018genome,hayes20191000,
Ros-Freixedes2020,karczewski2020mutational,tanjo2021practical,
halldorsson2022sequences} representing such uncertainty 
directly through the data structure is a useful alternative to 
classical methods based on probabilistic sampling.
